---
title: "JsonImport"
author: "ps.gilbert"
date: "June 17, 2015"
output: word_document
---
Import the json file into in R
```{r}
library(rjson)
stufftoprocessDOS<-fromJSON(file="/Users/Princess/Documents/Research/Aves/SignalNoise/Analyses/SignalNoise_TESTFOLDER/391_oryLat2.nex.rates")
```

Using jsonlite instead 
```{r}
library(jsonlite) # might need to load the package jsonlite. It's already downloaded to this compute and it's under "Packages on the right."
stufftoprocessDOS<-fromJSON(txt="/Users/Princess/Documents/Research/Aves/SignalNoise/Analyses/SignalNoise_TESTFOLDER/391_oryLat2.nex.rates.txt")

stufftoprocessDOSdataframe<-as.data.frame(stufftoprocessDOS)
tstuff<-transform(stufftoprocessDOSdataframe)
```

Isolate the substitution matrix values
```{r}
SubstitutionMatrix<-stufftoprocessDOS$sites$subs_matrix
```

Isolate the nucleotide frequencies
```{r}
NucleotideFrequencies<-stufftoprocessDOS$sites$freqs
```
Isolate the substitution per site rates
```{r}
RatesRates<-stufftoprocessDOS$sites$rates$rate
RatesRates_dataframe<-as.data.frame(RatesRates)
```
Export everything...
```{r}
#Base Pair Percentages
test_percents.txt<-write.table(testpercents[1:3], file="~/Documents/Research/Aves/SignalNoise/Analyses/SignalNoise_TESTFOLDER/Test_Percents.txt",col.names=c("PiA=", "PiC=", "PiT="),row.names=FALSE)
write.table(RatesRates,file="~/Documents/Research/Aves/SignalNoise/Analyses/SignalNoise_TESTFOLDER/Test_Rates.txt",row.names=FALSE)
()